---
title: "Application Exercise 4"
subtitle: "Research Design Submission" 
output: html_document
---

# R Markdown

## Headings

### Heading Level 3

#### Heading Level 4

## Markdown text

This is text written in markdown markup language. Markdown is written in **plain text** and produces formatted text. It's an **open format**, a file format with no restrictions, monetary or otherwise that can be fully processed with at least one free/libre/open-source software tool. As opposed to the .docx file format, which is a proprietary file format that a company owns and controls.

## Code chunks

Code chunks are added either by using a keyboard shortcut (Windows: Ctrl + Alt + I; MacOS: Cmd + Option + I) or by clicking on the green plus button in the menu bar of this file. 

```{r}

1 + 1

result <- 1 + 2

result

result * 2

sqrt(49)

sum(1, 2, 3)

text <- "some text"


```

Code is run either by a click on the green play button in the top right corner of the code chunk or by using a keyboard shortcut (Ctrl / Cmd + Enter) to execute code line by line. The code is sent to the Console where it is executed and the result is printed.

**Terminology**

- Assignment Operator: `<-`
- Function: `sum()`, `sqrt()`
- Object: Stored in current R session and can be viewed in 'Environment' Tab

## Inline code

You can also write code inline by using the single tick, followed by the letter r and the code. 

The sum of 1, 2, and 3 is `r sum(1, 2, 3)`. Or we can reuse the object we created above where we added 1 and 2, which makes `r result`. 

## Concept Map

I have included a concept map of R Markdown below [(Copyright (c) RStudio)](https://github.com/rstudio/concept-maps/blob/master/LICENSE.md) under licensed under [CC-BY](http://creativecommons.org/licenses/by/4.0/). You will learn how to use this code to include images as part of the course. 

```{r}
knitr::include_graphics("https://raw.githubusercontent.com/rstudio/concept-maps/master/en/rmarkdown.svg")
```

# Exercises

## Exercise 1 - Knit, Add, Commit, Push

1. **Knit:** Render this file to HTML (*Tip: Click the Knit Button at the top of this file*)
2. **Add** Open the Git pane and add all files to the staging area (*Tip: Tick off all checkboxes under column 'Staged'*)
3. **Commit:** Commit pending changes, add a meaningful commit message 
4. **Push:** Push changes to the remote repository (i.e. GitHub)

## Exercise 2 - Research Questions + Design

1. Add the research questions that you and/or your group have worked on below. Write a bullet point for each research question and sub-question.

**remove me and write your text here**

2. Write up the research design you are planning to use for your data collection.

**remove me and write your text here**

3. Write up the variables that are needed, together with the respective questions and possible response values.

**remove me and write your text here**

4. Knit, Add, Commit + Push your changes back to GitHub

## Exercise 3 - Hyperlinks and Equations (**Bonus**)

1. Use an online search engine to find the book "R Markdown: The Definitive Guide" and open it in your browser. 
2. Navigate to Section 2.5, read Sections 2.5.1, 2.5.2, and 2.5.3.
3. Use what you have learned to add a hyperlink below.
4. Use what you have learned to add an equation below.

**remove me and add a hyperlink**

**remove me and add an equation**

5. Knit, Add, Commit + Push your changes back to GitHub

## Exercise 4 - Output Options (**Bonus**)

1. Click on the gear icon next to the Knit button
2. Scroll down to 'Output Options...' and click. A new window opens.
3. Under 'General' tab, select to include a table of contents. 
4. Under 'General' tab, change the value at 'Apply theme:' from default to a theme of your choice.
5. Click OK to close the options window.
6. Scroll up to the YAML header to see what has changed.
7. Knit, Add, Commit + Push your changes back to GitHub

# Keyboard Shortcuts

Keyboard shortcuts are essential when working with any programming language and we recommend to use from the start instead of using the point + click buttons that are available in RStudio. 

- **Add new code chunk:** Ctrl/Cmd + Alt + I
- **Execute code line by line within a code chunk:** Ctrl/Cmd + Enter
- **Execute an entire code chunk:** Ctrl/Cmd + Shift + Enter
- **The Pipe (%>%):** Ctrl/Cmd + Shift + M
- **Assignment operator (<-)**: Alt/Option + -s


